Ecological network control

### 2018-06-18 paper/supp-info.Rmd
Kable tables must explicitly produce latex code

AICcmodavg::aictab(controllability_models) %>% 
  dplyr::mutate(Modnames = replace_terms(Modnames)) %>% 
  dplyr::select(Modnames, AICc, Delta_AICc, Cum.Wt) %>%
  dplyr::filter(Delta_AICc <= 8) %>%
  dplyr::rename(model = Modnames, `$\\Delta AICc$` = Delta_AICc, `$AICc$` = AICc, `Cum. Weight` = Cum.Wt) %>%
  dplyr::mutate(model = paste0("$", model, "$")) %>% 
  knitr::kable(escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with $\\Delta AIC < 8$ are shown.")
```

>>>>

AICcmodavg::aictab(controllability_models) %>% 
  dplyr::mutate(Modnames = replace_terms(Modnames)) %>% 
  dplyr::select(Modnames, AICc, Delta_AICc, Cum.Wt) %>%
  dplyr::filter(Delta_AICc <= 8) %>%
  dplyr::rename(model = Modnames, `$\\Delta AICc$` = Delta_AICc, `$AICc$` = AICc, `Cum. Weight` = Cum.Wt) %>%
  dplyr::mutate(model = paste0("$", model, "$")) %>% 
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with $\\Delta AIC < 8$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```
```
